\documentclass[12pt,a4paper]{article}
% Page layout and paras
\usepackage[top=2cm,left=3cm,right=3cm, bottom=1.5cm]{geometry}
\usepackage{parskip}

% Appendix
\usepackage{appendix}
\renewcommand{\appendixpagename}{\centerline{{\Large\bfseries Appendix}}}

% Colors
\usepackage{xcolor}
\definecolor{gr}{HTML}{007A5E}
\definecolor{bl}{HTML}{3366CC}

% Links
\usepackage[
breaklinks=true,
colorlinks=true,
% pagebackref=true,
linkcolor=gr,
citecolor=gr,
]{hyperref}

\newcommand{\refpp}[1]{\hyperref[#1]{LO~\ref{#1}}}
\newcommand{\pmk}[2]{\hypertarget{#1}{#2}}
\newcommand{\refpa}[1]{\hyperlink{para#1}{#1}}

% No indentation for paragraphs
\setlength\parindent{0pt}

\begin{document}

Dear CECC Student Services,

My name is Zhiren Lin (u7753813).  This short writing serves as a supplementary statement for my application to get the unspecified credit for the two university electives.

\subsection*{CoE and Study Visa not affected}
Since I am moving towards the last semester, getting these unspecified credits will have no impact on my study visa.  In the last semester, I will still need to enroll in two courses: COMP8715 (continued from this semester) and COMP8712 (my favorite subject and also to meet the program requirements\footnote{\url{https://programsandcourses.anu.edu.au/2023/program/7706xmcomp}}). I need to apply for reducing study load, though.


\subsection*{Previous full-time degree programs}
My previous two degree programs -- 5 years of full-time study at two different universities -- have covered a fairly wide range of topics and should make me eligible for two general university electives at ANU.

My bachelor degree program had a length of 4 years and required full-time study.  Such courses as Advanced Mathematics and Linear Algebra took 18 weeks in a normal 20-week semester. With common sense, all courses arranged in 4 years should add up to a total length far longer than 260 hours.

My first master degree program had a length of 12 months and required full-time study.  I have attached an example of the timetable\footnote{Open access at \url{http://timetablingunnc.nottingham.ac.uk:8017/program.htm}} for the entire program.  It is easy to see those courses together exceed 260 hours.

In addition, with 6-year work experience in several different jobs,  I am well aware of what skills and knowledge I have and lack.  The general electives would help me little with regard to my current study and future career.

\subsection*{Extra burden}
But they would place extra burden on me, both financially and mentally.

I am living in Weeden Lodge; my current room costs me \$517 fortnightly (or \$1142 monthly).  This means a single university elective alone costs approximately 4 or 6 months of rent, depending on what the course would be.  It is uncommon that a person would pay so much money for what they need so little.

If everything goes according to plan, I will be studying the compiler course in my last semester.  The course is probably among the most difficult and I do hope that I could fully dedicate myself to it in my last semester.  The two university electives will only make this almost impossible however.

In the last semester I will need to prepare for upcoming job interviews and necessary relocation.  These preparations and activities take non-trivial time and effort too.

I sincerely hope that I would have more time and freedom to focus on the courses and arrangements that are truly vital to my future career.  Thank you for reviewing my application.


\end{document}
